\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{xspace}

% use collab package
% hideedits: accept all edits and hide all edit marks
% hidecomments: hideedits and hide all comments
\usepackage[]{collab} %hideedits,hidecomments

% \yttty: the command of adding comments
% TY: the abbrevation that appears in the document
\newcommand{\yttty}[1]{\nbc{TY}{#1}{orange}}


\title{A 30-Second Readme for \texttt{collab.sty}}

\begin{document}
\maketitle

\section{Introduction}

\texttt{collab.sty} enables you to revise \LaTeX\xspace documents in a better way.

\section{Usage}
\subsection{usepackage command}
\noindent\emph{No macro: show all edits and comments.}
\begin{verbatim*}
\usepackage[]{collab}
\end{verbatim*}

\noindent\emph{\texttt{[hideedits]}: accept all edits and hide all edit marks.}
\begin{verbatim*}
\usepackage[hideedits]{collab}
\end{verbatim*}

\noindent\emph{\texttt{[hidecomments]}: \texttt{hideedits} + hide all comments}
\begin{verbatim*}
\usepackage[hidecomments]{collab}
\end{verbatim*}

\subsection{Define the comment}
\noindent\texttt{\\yttty}: the command of adding comments

\noindent\texttt{TY}: the abbrevation that appears in the document

\begin{verbatim*}
\newcommand{\yttty}[1]{\nbc{TY}{#1}{orange}}
\end{verbatim*}

\subsection{Syntax}
\subsubsection{Insertion}
Source Code:
\begin{verbatim}
insert \ins{something}
\end{verbatim}
Appearence: insert \ins{something}

\subsubsection{Deletion}
Source Code:
\begin{verbatim}
delete \del{something}
\end{verbatim}
Appearence: delete \del{something}

\subsubsection{Change}
Source Code:
\begin{verbatim}
change \chg{A}{to B}
\end{verbatim}
Appearence: change \chg{A}{to B}

\subsubsection{Wavy Lines}
Source Code:
\begin{verbatim}
\ugh{a worng wrod}
\end{verbatim}
Appearence: \ugh{a worng wrod}

\subsubsection{Comment}
Source Code:
\begin{verbatim}
\yttty{This is a comment.}
\end{verbatim}
Appearence: \yttty{This is a comment.}

\section{Example}

LaTeX is a software system for document preparation. When writing, the writer uses \del{truely} \yttty{Conciseness!} plain text as opposed to the formatted text found in "What You See Is What You Get" word processors like Microsoft Word, LibreOffice Writer \ins{and Apple Pages}.

You don't have to pay for using LaTeX, i.e., there are \chg{high}{no} license fees, etc. But you are, of course, invited to \ugh{support the maintenance and development efforts} through a donation to the TeX Users Group (choose LaTeX Project contribution) if you are satisfied with LaTeX \yttty{Please consider a donation!}.

\end{document}
